library(survival)
library(blantyreSepsis)
library(dplyr)
library(tidyr)
library(stringr)
library(forcats)
library(purrr)
library(kableExtra)
library(ggplotify)
library(UpSetR)
library(eulerr)
library(patchwork)
library(survminer)
library(wBoot)
library(viridis)
library(brms)
library(pheatmap)
library(factoextra)
library(mice)
library(bayesplot)
library(splines)
library(here)



# transform

BTparticipants %>%
  select(
    ustand,
    calc_age,
    ptsex,
    hivstatus,
    cd4_absolute,
    haemoglobin,
    screentemp,
    t0sbp,
    t0dbp,
    t0hr,
    t0rr,
    t0spo2,
    gcs,
    lactate,
    wcc,
    platelets,
    sodium,
    co2,
    creatinine,
    urea
  ) %>%
  mutate(
    male = if_else(ptsex == "Male", 1, 0),
    hiv_reactive = case_when(
      hivstatus == "Reactive" ~ 1,
      hivstatus == "Non reactive" ~ 0,
      TRUE ~ NA_real_
    ),
    gcs.low = as.numeric(gcs < 15)
  ) %>%
  select(-c(ptsex, hivstatus, gcs))  ->
  df.mod.trans
df.mod.trans[df.mod.trans== 999] <- NA



df.mod.trans %>%
  mutate(
    calc_age_log = log(calc_age),
    cd4_absolute_log = log(cd4_absolute),
    creatinine_log = log(creatinine),
    lactate_log = log(lactate),
    plt_log = log(platelets),
    t0spo2_log = log(101 - t0spo2),
    t0sbp_log = log(t0sbp),
    t0dbp_log = log(t0dbp),
    urea_log = log(urea),
    screentemp_log = log(41 - screentemp),
    wcc_log = log(wcc),
    sodium_log = log(sodium),
    t0rr_log = log(t0rr)
  ) -> df.mod.trans

df.mod.trans %>%
  pivot_longer(everything()) %>%
  ggplot(aes(value)) +
  geom_density() +
  facet_wrap( ~ name, scales = "free")

# drop unused vars

df.mod.trans %>%
  select(
    -c(
      cd4_absolute,
      creatinine,
      lactate,
      platelets,
      t0spo2,
      t0sbp,
      t0dbp,
      t0rr_log,
      screentemp,
      urea,
      t0dbp,
      sodium,
      wcc,
      calc_age
    )
  ) -> df.mod.trans


# rename and drop diastolic blood pressure and urea
# because strongly correlated with systolic blood pressure and creatinine

df.mod.trans %>%
  dplyr::rename(
    Age = calc_age_log,
    CD4 = cd4_absolute_log,
    Lactate = lactate_log,
    Cr = creatinine_log,
    Plt = plt_log,
    SpO2 = t0spo2_log,
    SBP = t0sbp_log,
    Temp = screentemp_log,
    WCC = wcc_log,
    RR = t0rr,
    Hb = haemoglobin,
    `HIV+` = hiv_reactive,
    HR = t0hr,
    Male = male,
    `GCS<15` = gcs.low,
    Na = sodium_log,
    `HCO3-` = co2,
    CantStand = ustand
  ) %>%
  select(-c(t0dbp_log,
            urea_log)) ->
  df.mod.trans



### Perform PCA



# do PCA

# first prepare full df with all necessary covariates for modelling

# Prepare data frame with all metaadata --------------------------------
# remember df.mod.trans is all the transformed covariates for PCA
# BTdata_combined is all data


BTparticipants %>%
  select(-c(
    d90_death,
    d180_death,
    t,
    died,
    art_time,
    hivcpt,
    ever_tb,
    tbongoing
  )) %>%
  left_join(
    BTtreatment %>%
      transmute(
        pid = pid,
        tb.rx = !is.na(timeto_antitb),
        fung.rx = !is.na(timeto_antifungal),
        mal.rx = !is.na(timeto_antimalarial),
        time_to_abx = timeto_ab,
        fluid.6hr = iv_fluid_6hr
      )
  ) %>%
  left_join(
    select(
      BTaetiology,
      pid,
      malaria,
      dengue,
      chik,
      arbovirus,
      inv.bacterial,
      inv.fungal,
      tb
    ) %>%
      mutate(across(!contains("pid"), ~ if_else(is.na(
        .x
      ), 0, .x)))
  ) %>%
  mutate(
    ustand = as.character(ustand),
    malaria = as.character(malaria),
    dengue = as.character(dengue),
    chik = as.character(chik),
    inv.bacterial = as.character(inv.bacterial),
    inv.fungal = as.character(inv.fungal),
    tb = as.character(tb),
    tb.rx = as.character(as.numeric(tb.rx)),
    fung.rx = as.character(as.numeric(fung.rx)),
    mal.rx = as.character(as.numeric(mal.rx)),
    time_to_abx = as.numeric(time_to_abx),
    abx = as.character(as.numeric(!is.na(time_to_abx))),
    fluid.6hr = fluid.6hr / 1000,
    d28_death = as.character(d28_death),
    ptsex = recode(ptsex,
                   "Male" = "1",
                   "Female" = "0"),
    hivstatus = recode(
      hivstatus,
      "Reactive" = "1",
      "Non reactive" = "0",
      .default = NA_character_
    ),
  ) %>%
  mutate(
    no_diagnosis = 1,
    no_diagnosis = case_when(
      malaria == 1 ~ 0,
      dengue == 1 ~ 0,
      chik == 1 ~ 0,
      inv.bacterial == 1 ~ 0,
      inv.fungal == 1 ~ 0,
      tb == 1 ~ 0,
      TRUE ~ no_diagnosis
    ),
    no_diagnosis = as.character(no_diagnosis),
    tb = if_else(is.na(tb), "0", tb),
    malaria = if_else(is.na(malaria), "0", malaria),
    dengue = if_else(is.na(dengue), "0", dengue),
    chik = if_else(is.na(chik), "0", chik),
    inv.bacterial = if_else(is.na(inv.bacterial), "0", inv.bacterial),
    inv.fungal = if_else(is.na(inv.fungal), "0", inv.fungal)
  ) ->
  BTdata_combined

# do PCA -----------------------------------------------------------------
# on df,mod.trans

prcomp(df.mod.trans[complete.cases(df.mod.trans),],
       scale = TRUE) -> p

p.scores <- as.data.frame(p$scores)

# add in metadata: 28 day death  
  
bind_cols(
  BTdata_combined[complete.cases(df.mod.trans),] %>% 
    select(d28_death),
  as.data.frame(p$x)
) -> p.out







priors <- c(
  prior(student_t(3, 0, 2.5), class = "Intercept"),
  prior(student_t(3, 0, 2.5), class = "b")
)

brm(
  formula = d28_death ~ PC1 +
    PC2  +
    PC3,
  data = p.out, prior = priors,
  family = bernoulli(link = "logit"), save_all_pars = TRUE
)-> b.mod3




### Impute missing data

```{r impute-missing-data}
# Scale fluid and time to abx --------------------------------------------

fluid.mean <- mean(BTdata_combined$fluid.6hr, na.rm = TRUE)
fluid.sd <- sd(BTdata_combined$fluid.6hr, na.rm = TRUE)
BTdata_combined$fluid.6hr <- (BTdata_combined$fluid.6hr - 
                                fluid.mean)/fluid.sd
tta.mean <- mean(BTdata_combined$time_to_abx, na.rm = TRUE)
tta.sd <- sd(BTdata_combined$time_to_abx, na.rm = TRUE)
BTdata_combined$time_to_abx <- (BTdata_combined$time_to_abx- 
                                  tta.mean)/tta.sd

# Prepare datafrane for imputation

bind_cols(
  df.mod.trans,
  BTdata_combined %>% 
    select(
      d28_death,
      pid,
      tb.rx,
      fung.rx,
      mal.rx,
      malaria, 
      arbovirus, 
      inv.bacterial, 
      inv.fungal, 
      tb,
      time_to_abx,
      fluid.6hr)) %>% 
  mutate(
    CantStand = as.character(CantStand),
    `HIV+` = as.factor(`HIV+`),
    `GCS<15` = as.factor(`GCS<15`),
    d28_death = as.factor(d28_death),
    tb = as.numeric(tb),
    tb = if_else(is.na(tb), 0, tb),
    malaria = as.numeric(malaria),
    malaria = if_else(is.na(malaria), 0, malaria),
    arbovirus = as.numeric(arbovirus),
    arbovirus = if_else(is.na(arbovirus), 0, arbovirus),
    inv.bacterial = as.numeric(inv.bacterial),
    inv.bacterial = if_else(is.na(inv.bacterial), 0, inv.bacterial),
    inv.fungal = as.numeric(inv.fungal),
    inv.fungal = if_else(is.na(inv.fungal), 0, inv.fungal),
  ) %>%
  dplyr::rename(
    HIV_pos = `HIV+`,
    GCS_less15 = `GCS<15`,
    HCO3 = `HCO3-`
  ) %>% 
  as.data.frame() ->
  df.mod.trans.scale.plus.metadata

# make pred matrix ----------------------------------------------------------

# predict everything from everything else

mice(df.mod.trans.scale.plus.metadata, maxit = 0) -> ini
pm <- ini$predictorMatrix
ini$method -> meth
pm[, (ncol(df.mod.trans) + 2):ncol(df.mod.trans.scale.plus.metadata)] <- 0
pm[(ncol(df.mod.trans) + 2):ncol(df.mod.trans.scale.plus.metadata),] <- 0
meth[(ncol(df.mod.trans) + 2):ncol(df.mod.trans.scale.plus.metadata)] <- ""
df.mod.trans.scale.plus.metadata$time_to_abx <- as.numeric(
  df.mod.trans.scale.plus.metadata$time_to_abx
)

# impute missing data --------------------------------------------------------

m <- 10 # number of datasets
mice(df.mod.trans.scale.plus.metadata, m = m, predictorMatrix = pm,
     method = meth) -> df.mod.imp
complete(df.mod.imp, action = "all") -> datasets.imp

### Scale imputed data and project onto PCA coordinates


# get variables to correct type -----------------------------------------------

lapply(datasets.imp,
       function(x)
         x %>% mutate(
           CantStand = as.numeric(CantStand),
           HIV_pos = as.numeric(HIV_pos),
           GCS_less15 = as.numeric(GCS_less15),
           d28_death = as.numeric(d28_death),
           d28_death = d28_death - 1,
           tb = as.factor(tb),
           tb.rx = as.factor(tb.rx),
           malaria = as.factor(malaria),
           inv.fungal = as.factor(inv.fungal)
         ) %>%
         as.data.frame) -> datasets.imp

# project onto pca coords ----------------------------------------------------

lapply(datasets.imp,
       function(x)
         bind_cols(
           x,
           as.data.frame(
             scale(x[,1:ncol(df.mod.trans)],
                 p$center, p$scale) %*% p$rotation) 
         )) -> datasets.imp

# add the mice .imp and .id vars back in -------------------------------------

for (i in 1:m) {
    datasets.imp[[i]]$.imp <- i
    datasets.imp[[i]]$.id <- 1:nrow(datasets.imp[[i]])
  }


### Fit models for antimicrobial therapy

# fit univariable and then multivariable models -------------------------------

# tb ----------------------------------------------------------------------

# univrariable - diagnosis

brm_multiple(
  formula = d28_death ~
    tb,
  prior = priors,
  data = datasets.imp,
  family = bernoulli(link = "logit"),
  save_all_pars = TRUE
) -> b.m.tb.unadj
#write_rds(b.m.tb.unadj, "models/b.m.tb.unadj.RDS")

# univrariable - treatment

brm_multiple(
  formula = d28_death ~
    tb.rx,
  prior = priors,
  data = datasets.imp,
  family = bernoulli(link = "logit"),
  save_all_pars = TRUE
) -> b.m.tb.rx.unadj
#write_rds(b.m.tb.rx.unadj, "models/b.m.tb.rx.unadj.RDS")

# multivariable

brm_multiple(
  formula = d28_death ~ PC1 +
    PC2  +
    PC3 +
    tb + tb.rx,
  prior = priors,
  data = datasets.imp,
  family = bernoulli(link = "logit"),
  save_all_pars = TRUE
) -> b.m.tb
#write_rds(b.m.tb, "models/b.m.tb.final.RDS")


#mcmc_intervals_data(b.m.tb, regex_pars = "^b_", 
#transformations = exp, prob_outer = 0.95)

# malaria --------------------------------------------------------------------

# multivariable 

brm_multiple(
  formula = d28_death ~ PC1 +
    PC2  +
    PC3 +
    malaria + mal.rx,
  prior = priors,
  data = datasets.imp,
  family = bernoulli(link = "logit"),
  save_all_pars = TRUE
) -> b.m.mal
#write_rds(b.m.mal, "models/b.m.mal.final.RDS")

# univariable - diagnosis

brm_multiple(
  formula = d28_death ~
    malaria,
  prior = priors,
  data = datasets.imp,
  family = bernoulli(link = "logit"),
  save_all_pars = TRUE
) -> b.m.mal.univ
#write_rds(b.m.mal.univ, "models/b.m.mal.univ.RDS")

# univariable - treatment

brm_multiple(
  formula = d28_death ~
    mal.rx,
  prior = priors,
  data = datasets.imp,
  family = bernoulli(link = "logit"),
  save_all_pars = TRUE
) -> b.m.mal.rx.univ
#write_rds(b.m.mal.rx.univ, "models/b.m.mal.rx.univ.RDS")
#mcmc_intervals_data(b.m.mal, regex_pars = "^b_",
#transformations = exp, prob_outer = 0.95)

# invasive fungal ----------------------------------------------------------

# multivariable

brm_multiple(
  formula = d28_death ~ PC1 +
    PC2  +
    PC3 +
    inv.fungal + fung.rx,
  prior = priors,
  data = datasets.imp,
  family = bernoulli(link = "logit"),
  save_all_pars = TRUE
) -> b.m.fung
#write_rds(b.m.fung, "models/b.m.fung.final.RDS")

# diagnosis

brm_multiple(
  formula = d28_death ~
    inv.fungal,
  prior = priors,
  data = datasets.imp,
  family = bernoulli(link = "logit"),
  save_all_pars = TRUE
) -> b.m.fung.univ
#write_rds(b.m.fung.univ, "models/b.m.fung.univ.RDS")

brm_multiple(
  formula = d28_death ~ fung.rx,
  prior = priors,
  data = datasets.imp,
  family = bernoulli(link = "logit"),
  save_all_pars = TRUE
) -> b.m.fung.rx.univ
#write_rds(b.m.fung.rx.univ, "models/b.m.fung.rx.univ.RDS")

# make output df -----------------------------------------------------------

bind_rows(
  mcmc_intervals_data(
    b.mod3,
    regex_pars = "^b_",
    transformations = exp,
    prob_outer = 0.95
  ) %>%
    filter(str_detect(parameter, "_PC")) %>%
    mutate(type = "unadjusted",
           adj = "unadjusted"),
  mcmc_intervals_data(
    b.m.tb.unadj,
    regex_pars = "^b_",
    transformations = exp,
    prob_outer = 0.95
  ) %>%
    filter(str_detect(parameter, "tb")) %>%
    mutate(type = "unadjusted",
           adj = "unadjusted"),
  mcmc_intervals_data(
    b.m.tb.rx.unadj,
    regex_pars = "^b_",
    transformations = exp,
    prob_outer = 0.95
  ) %>%
    filter(str_detect(parameter, "tb")) %>%
    mutate(type = "unadjusted",
           adj = "unadjusted"),
  mcmc_intervals_data(
    b.m.tb,
    regex_pars = "^b_",
    transformations = exp,
    prob_outer = 0.95
  ) %>%
    filter(str_detect(parameter, "tb") |
             str_detect(parameter, "_PC")) %>%
    mutate(type = "tb.model",
           adj = "adjusted"),
  mcmc_intervals_data(
    b.m.mal.univ,
    regex_pars = "^b_",
    transformations = exp,
    prob_outer = 0.95
  ) %>%
    filter(str_detect(parameter, "mal")) %>%
    mutate(type = "unadjusted",
           adj = "unadjusted"),
  mcmc_intervals_data(
    b.m.mal.rx.univ,
    regex_pars = "^b_",
    transformations = exp,
    prob_outer = 0.95
  ) %>%
    filter(str_detect(parameter, "mal")) %>%
    mutate(type = "unadjusted",
           adj = "unadjusted"),
  mcmc_intervals_data(
    b.m.mal,
    regex_pars = "^b_",
    transformations = exp,
    prob_outer = 0.95
  ) %>%
    filter(str_detect(parameter, "mal") |
             str_detect(parameter, "_PC")) %>%
    mutate(type = "mal.model",
           adj = "adjusted"),
  mcmc_intervals_data(
    b.m.fung.univ,
    regex_pars = "^b_",
    transformations = exp,
    prob_outer = 0.95
  ) %>%
    filter(str_detect(parameter, "fung")) %>%
    mutate(type = "unadjusted",
           adj = "unadjusted"),
  mcmc_intervals_data(
    b.m.fung.rx.univ,
    regex_pars = "^b_",
    transformations = exp,
    prob_outer = 0.95
  ) %>%
    filter(str_detect(parameter, "fung")) %>%
    mutate(type = "unadjusted",
           adj = "unadjusted"),
  mcmc_intervals_data(
    b.m.fung,
    regex_pars = "^b_",
    transformations = exp,
    prob_outer = 0.95
  ) %>%
    filter(str_detect(parameter, "fung") |
             str_detect(parameter, "_PC")) %>%
    mutate(type = "fung.model",
           adj = "adjusted")  
) -> df.plot

```

```{r plot-model-outputs, fig.cap = "Unadjusted and adjusted odds ratios for death for antimicrobial treatments.", fig.height = 5, fig.width= 5 }

# Plot effects of antimicrobial treatments

df.plot %>% 
  filter(!(str_detect(parameter, "_PC") & adj == "adjusted")) %>% 
  filter((str_detect(parameter, "rx1") | str_detect(parameter, "PC"))) %>% 
  mutate(parameter =
           case_when(
             str_detect(parameter, "fung.rx") ~ "Antifungal",
             str_detect(parameter, "mal.rx") ~ "Antimalarial",
             str_detect(parameter, "tb.rx") ~ "Antimtubercular",
             TRUE ~ str_replace(parameter, "t\\(b_", "")
           )) %>% 
  mutate(parameter = str_replace(parameter, "\\)", "")
  ) %>% 
  ggplot(aes(parameter, 
             m, 
             ymin = ll, 
             ymax = hh, 
             color = fct_rev(adj),
             shape = fct_rev(adj))) + 
  geom_point(position = position_dodge(width = 0.4)) + 
  geom_errorbar(width = 0,position = position_dodge(width = 0.4)) + 
  theme_bw() +
  geom_hline(aes(yintercept = 1), linetype = "dashed") +
  labs(y = "OR", x = "Antimicrobial")  +
  theme(legend.position = "top", 
        legend.title = element_blank(),
        axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_color_manual(values = c(
                                viridis(6, option = "C")[4],
                                "black")) +
  scale_shape_manual(values = c(4, 16))-> p.effects

p.effects


### Fit models for time-to-antibacterials and vlume of IV fluid

# models for time to antibacterials (linear and restricted cubic spline) ------
# and IV fluid (linear and restricted cubic spline) ------------------

# time to abx ----------------------------------------------------------

# linear time to abx univariable

brm_multiple(
  formula = d28_death ~   time_to_abx,
  prior = priors,
  data = datasets.imp,
  family = bernoulli(link = "logit"),
  save_all_pars = TRUE
) -> b.m.tta.lin.univ

#write_rds(b.m.tta.lin.univ, "models/b.m.tta.lin.univ.RDS")
#exp(mcmc_intervals_data(b.m.tta.lin.univ,  regex_pars = "^b",
#                        prob_outer = 0.95)[5:9]/tta.sd)

# linear time to abx corrected for severity/host

brm_multiple(
  formula = d28_death ~ PC1 +
    PC2  +
    PC3 +
    time_to_abx,
  prior = priors,
  data = datasets.imp,
  family = bernoulli(link = "logit"),
  save_all_pars = TRUE
) -> b.m.tta.lin
#write_rds(b.m.tta.lin, "models/b.m.tta.lin.RDS")
#exp(mcmc_intervals_data(b.m.tta.lin,  regex_pars = "^b",
#                    prob_outer = 0.95)[5,5:9]/tta.sd)



# restricted cubic spline time to abx
# calculate quantiles for knots
k <- quantile(datasets.imp[[1]]$time_to_abx,
              c(0.1, 0.5, 0.9),
              na.rm = TRUE)

# fit
brm_multiple(
  formula = d28_death ~ PC1 +
    PC2  +
    PC3 +
    ns(time_to_abx,
       knots = c(-0.599, -0.418, 1.028)),
  prior = priors,
  data = datasets.imp,
  family = bernoulli(link = "logit"),
  save_all_pars = TRUE
) -> b.m.tta.nonlin
#write_rds(b.m.tta.nonlin, "models/b.m.tta.nonlin.RDS")

# IV fluid ---------------------------------------------------------- 
# restricted cubic spine, corrected for severity/host

# get knot locations
k <- quantile(datasets.imp[[1]]$fluid.6hr,
              c(0.1, 0.5, 0.9),
              na.rm = TRUE)

# fit

brm_multiple(
  formula = d28_death ~ PC1 +
    PC2  +
    PC3 + ns(fluid.6hr, knots = c(-1.564, -0.009, 1.410)),
  prior = priors,
  data = datasets.imp,
  family = bernoulli(link = "logit"),
  save_all_pars = TRUE
) -> b.m.fluid
#write_rds(b.m.fluid, "models/b.m.fluid.RDS")

# linear corrected for severity/host

brm_multiple(
  formula = d28_death ~ PC1 +
    PC2  +
    PC3 + fluid.6hr,
  prior = priors,
  data = datasets.imp,
  family = bernoulli(link = "logit"),
  save_all_pars = TRUE
) -> b.m.fluid.lin

# univariable 

brm_multiple(
  formula = d28_death ~ fluid.6hr,
  prior = priors,
  data = datasets.imp,
  family = bernoulli(link = "logit"),
  save_all_pars = TRUE  
) -> b.m.fluid.lin.univ

#write_rds(b.m.fluid.lin, "models/b.m.fluid.lin.RDS")
#write_rds(b.m.fluid.lin.univ, "models/b.m.fluid.lin.univ.RDS")
#exp(mcmc_intervals_data(b.m.fluid.lin.univ,  regex_pars = "^b",
#                        prob_outer = 0.95)[5:9]*1000/fluid.sd)
#exp(mcmc_intervals_data(b.m.fluid.lin,  regex_pars = "^b",
#                        prob_outer = 0.95)[5,5:9]*1000/fluid.sd)

# plot marginal effects -----------------------------------------------------

conditional_effects(b.m.tta.nonlin, effects = "time_to_abx") -> tta.ce

tta.ce$time_to_abx %>% 
  ggplot(aes((time_to_abx + tta.mean/tta.sd)*tta.sd, 
             estimate__, ymin = lower__, ymax = upper__)) + 
  geom_line() + 
  geom_ribbon(alpha = 0.3, fill = viridis(6, option = "C")[4])  + 
  coord_cartesian(ylim = c(0,0.3), xlim = c(0,50)) + 
  theme_bw() + labs(x = "Time (hrs) to antibacterial", 
                    y = "28-day mortality") -> p.tta

conditional_effects(b.m.fluid, effects = "fluid.6hr") -> fluid.ce

fluid.ce$fluid.6hr %>% 
  ggplot(aes((fluid.6hr + fluid.mean/fluid.sd)*(fluid.sd), 
             estimate__, ymin = lower__, ymax = upper__)) + geom_line() + 
  geom_ribbon(alpha = 0.3, fill = viridis(6, option = "C")[4])  + 
  coord_cartesian(ylim = c(0,0.3)) + 
  theme_bw() + 
  labs(x = "Fluid (L) over 6hr", y = "28-day mortality") -> p.fluid


(p.fluid | p.tta ) + plot_annotation(tag_levels = "A")



### Final parameter estimate table

# Make table of model outputs
bind_rows(
  df.plot,
  mcmc_intervals_data(
    b.m.tta.lin.univ,
    regex_pars = "^b_",
    prob_outer = 0.95
  ) %>%
    dplyr::mutate(across(
      starts_with(c("l", "m", "h")),
      ~ case_when(parameter == "b_time_to_abx" ~
                    exp(.x / tta.sd),
                  TRUE ~ exp(.x))
    )) %>%
    filter(str_detect(parameter, "abx") |
             str_detect(parameter, "_PC")) %>%
    mutate(type = "unadjusted",
           adj = "unadjusted"),
  mcmc_intervals_data(b.m.tta.lin,
                      regex_pars = "^b_",
                      prob_outer = 0.95) %>%
    dplyr::mutate(across(
      starts_with(c("l", "m", "h")),
      ~ case_when(parameter == "b_time_to_abx" ~
                    exp(.x / tta.sd),
                  TRUE ~ exp(.x))
    )) %>%
    filter(str_detect(parameter, "abx") |
             str_detect(parameter, "_PC")) %>%
    mutate(type = "tta.model",
           adj = "adjusted"),
  mcmc_intervals_data(
    b.m.fluid.lin.univ,
    regex_pars = "^b_",
    prob_outer = 0.95
  ) %>%
    dplyr::mutate(across(
      starts_with(c("l", "m", "h")),
      ~ case_when(parameter == "b_fluid.6hr" ~
                    exp(.x / fluid.sd),
                  TRUE ~ exp(.x))
    )) %>%
    filter(str_detect(parameter, "fluid") |
             str_detect(parameter, "_PC")) %>%
    dplyr::mutate(type = "unadjusted",
                  adj = "unadjusted"),
  mcmc_intervals_data(b.m.fluid.lin,
                      regex_pars = "^b_",
                      prob_outer = 0.95) %>%
    dplyr::mutate(across(
      starts_with(c("l", "m", "h")),
      ~ case_when(parameter == "b_fluid.6hr" ~
                    exp(.x / fluid.sd),
                  TRUE ~ exp(.x))
    )) %>%
    filter(str_detect(parameter, "fluid") |
             str_detect(parameter, "_PC")) %>%
    mutate(type = "fluid.model",
           adj = "adjusted")
) ->
  df.plot


df.plot %>%
  mutate(parm_string = paste0(sp_dc(m, 2), " (", sp_dc(ll, 2),
                              "-", sp_dc(hh, 2), ")")) %>%
  mutate(parameter = str_replace(parameter, "t\\(b_|b_", "")) %>%
  mutate(
    parameter = str_replace(parameter, "\\)", "")
    ) %>% 
  select(parameter, parm_string, type, adj) %>%
  pivot_wider(
    id_cols = parameter,
    names_from = c(type, adj),
    values_from = parm_string
  ) -> mod.output.tab


mod.output.tab %>% 
  dplyr::mutate(
    parameter = dplyr::recode(
      parameter,
      tb1 = "Diagnosis is TB",
      tb.rx1 = "Received TB treatment",
      malaria1 = "Diagnosis is malaria",
      mal.rx1 = "Received malaria treatment",
      inv.fungal1 =
        "Diagnosis is invasive fungal disease",
      fung.rx1 = "Recieved antifungal",
      time_to_abx = "Time to antibacterial therapy (per hour)",
      fluid.6hr = "Vol of IV fluid (L)"
    )
  ) %>%
  dplyr::rename(
    "Unadjusted" = "unadjusted_unadjusted",
    "TB treatment" = "tb.model_adjusted",
    "Malaria treatment" = "mal.model_adjusted",
    "Fungal treatment" = "fung.model_adjusted",
    "Time to antibacterial" = "tta.model_adjusted",
    "Vol of IV fluid" = "fluid.model_adjusted"
  ) %>%
  dplyr::mutate(
    dplyr::across(
      dplyr::everything(),
      ~ if_else(is.na(.x), "-", .x)
      )
    ) -> mod.output.tab

kbl(mod.output.tab,
    row.names = F, caption = "SUPPLEMENTARY TABLE 8: Parameter estimates from models assessing effect of therapies on mortality, expressed as adjusted odds ratios with a point estimate (posterior median) and 95% credible intervals.") %>%
  kable_classic(full_width = FALSE)

#write_csv(mod.output.tab, "tables/SUP_mort_models_table.csv")

### Final publication plot


# (1,2) PCA var plot and final mort plot  ------------------------------------


(p.effects | p.tta | p.fluid) + 
  plot_annotation(tag_levels = "A") 

mort.model.plot.final
if (write_figs) {
  
ggsave( here("figures/MAIN_F3_mort_model.plot.pdf"),
        mort.model.plot.final, 
        width = 8, height = 8, units = "in")
ggsave( here("figures/MAIN_F3_mort_model.plot.tiff"),
        mort.model.plot.final, 
        width = 8, height = 8, units = "in",
        dpi = 600)
}
```



### Reproducability

```{r sessioninfo}

sessionInfo()

```
